Convective penetration probably parameterizes convective overshoot

### 2021-07-20 manuscript/ms.tex
incorporates comments from Adam in sct 6

Our simulation results present a strong case for a flux- and dissipation-based model of convective penetration, similar to those considered by \citet{zahn1991} and \citet{roxburgh1989}.
In order to implement our theory into MESA, we need to extend Eqn.~\ref{eqn:theory_fraction} to spherical geometry.
To do so, we replace horizontal averages in Eqn.~\ref{eqn:integral_constraint} with integrals over latitude and longitude, and find that the relevant integral constraint contains the convective luminosity,
\begin{equation}
\int |\alpha| g L_{\rm{conv}}\,dr =   \int_V \rho_0 \Phi\,dV,
\end{equation}
where $L_{\rm{conv}} = 4\pi\rho_0 r^2 \bar{F_{\rm{conv}}}$, $r$ is the radial coordinate, and we write the RHS as a volume integral.
We next define $f$ in the same way as in Eqn.~\ref{eqn:f_defn} and define $\xi$ similarly to Eqn.~\ref{eqn:xi_defn},
\begin{equation}
\int_{\rm{PZ}} \rho_0 \Phi \,dV = \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}}\int_{\rm{CZ}}\rho_0 \Phi \, dV,
\label{eqn:sphere_xi_defn}
\end{equation}
where $V_{\rm{PZ}}$ and $V_{\rm{CZ}}$ are the volumes of the CZ and PZ respectively.
Eqn.~\ref{eqn:sphere_xi_defn} generalizes Eqn.~\ref{eqn:xi_defn} outside of the assumption of a plane-parallel atmosphere.
Thus Eqn.~\ref{eqn:theory_fraction} in spherical geometry is
\begin{equation}
-\frac{\int_{\rm{PZ}} L_{\rm{conv}}\,dr}{\int_{\rm{CZ}} L_{\rm{conv}}\,dr} + f \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}} = (1 - f),
\label{eqn:mesa_eqn}
\end{equation}

@@

At the Schwarzschild base of the CZ, we find $H_p \approx 0.082R_\odot$, and the depth of the penetration zone in Fig.~\ref{fig:mesa_profiles} is $0.042R_\odot$, such that this PZ extends $\sim 50$\% of a scale height below the convection zone.
Helioseismic studies have suggested that a PZ depth should be constrained to 5-10\% of $H_P$ \citep{basu_etal_1994, basu2016}; these constraints are significantly smaller than our crude model.
Some recent simulations \citep{kapyla2019} have suggested that solar convection could exhibit penetration depths of $0.2 H_P$, which are closer to these models but still smaller than what we measure.
Despite these discrepancies, Fig.~\ref{fig:mesa_profiles} shows the promise of a convective penetration parameterization such as the one presented here.
Pathways for improving our parameterization will be discussed in the following section.

@@

To find the extent of the penetrative region we write Eqn.~\eqref{eq:mesa_eqn} as
\begin{align}
	(1-f) \int_{\rm CZ} L_{\rm conv} dr = \int_{\rm PZ} \xi f L_{\rm conv,avg,CZ} + L_{\rm conv} dr,
	\label{eq:rwt}
\end{align}
where $L_{\rm conv,avg,CZ}$ is the average of $L_{\rm conv}$ in the convection zone and $L_{\rm conv}$ in the penetrative region is given by
\begin{align}
	L_{\rm conv} = \frac{L_{\rm rad}}{\nabla_r}(\nabla_a - \nabla_r),
\end{align}
which is the excess luminosity carried if the temperature gradient in the radiative zone is adiabatic.

@@

\newpage
\section{Table of simulation parameters}
\label{app:simulation_table}
Input parameters and summary statistics of the simulations presented in this work are shown in Table~\ref{table:simulation_info}.

@@

\bibliographystyle{aasjournal}
\bibliography{biblio}
\end{document}

>>>>

Our simulation results present a strong case for a flux- and dissipation-based model of convective penetration, similar to those considered by \citet{zahn1991} and \citet{roxburgh1989}.
In order to implement our theory into MESA, we need to extend Eqn.~\ref{eqn:theory_fraction} to spherical geometry.
To do so, we replace horizontal averages in Eqn.~\ref{eqn:integral_constraint} with integrals over latitude and longitude, and find that the relevant integral constraint contains the convective luminosity,
\begin{equation}
\int |\alpha| g L_{\rm{conv}}\,dr =   \int_V \rho_0 \Phi\,dV,
\label{eqn:mesa_integral_constraint}
\end{equation}
where $L_{\rm{conv}} = 4\pi\rho_0 r^2 \bar{F_{\rm{conv}}}$, $r$ is the radial coordinate, and we write the RHS as a volume integral.
We next define $f$ in the same way as in Eqn.~\ref{eqn:f_defn} and define $\xi$ similarly to Eqn.~\ref{eqn:xi_defn},
\begin{equation}
\int_{\rm{PZ}} \rho_0 \Phi \,dV = \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}}\int_{\rm{CZ}}\rho_0 \Phi \, dV,
\label{eqn:sphere_xi_defn}
\end{equation}
where $V_{\rm{PZ}}$ and $V_{\rm{CZ}}$ are the volumes of the CZ and PZ respectively.
Eqn.~\ref{eqn:sphere_xi_defn} generalizes Eqn.~\ref{eqn:xi_defn} outside of the assumption of a plane-parallel atmosphere.
Thus Eqn.~\ref{eqn:theory_fraction} in spherical geometry is
\begin{equation}
-\frac{\int_{\rm{PZ}} L_{\rm{conv}}\,dr}{\int_{\rm{CZ}} L_{\rm{conv}}\,dr} + f \xi \frac{V_{\rm{PZ}}}{V_{\rm{CZ}}} = (1 - f),
\label{eqn:mesa_eqn}
\end{equation}

@@

When a PZ is present beneath a CZ, $\justgrad$ experiences a sharp jump from $\gradad$ to $\gradrad$ (Fig.~\ref{fig:mesa_profiles}, top panel), resulting in an acoustic ``glitch'' in the sound speed profile (Fig.~\ref{fig:mesa_profiles}, bottom panel).
Helioseismic studies have argued that that the solar PZ depth cannot be larger than $\mathcal{O}$(0.05 $H_p$), because larger PZs would result in larger glitches than are detected  \citep[see Sct.~7.2.1 of][for a nice review]{basu2016}.
However, some recent 3D convective simulations by \citet{kapyla2019} suggest that the solar PZ depth could be as large as $\mathcal{O}(0.2 H_p)$.
In the model shown in Fig.~\ref{fig:mesa_profiles}, we find $H_p \approx 0.082R_\odot$ at the Schwarzschild CZ boundary, and the depth of the penetration zone in Fig.~\ref{fig:mesa_profiles} is $0.042R_\odot \sim 0.5 H_p$.
This over-estimates fully compressible simulations by a factor of a few, and observations by an order of magnitude.
However, it is unsurprising that our Boussinesq-based model only qualitatively matches observational constraints for the solar CZ.
The solar convection zone is highly stratified ($\sim$14 density scale heights), and we neglected density stratification in this work.
Fig.~\ref{fig:mesa_profiles} shows that our parameterization can produce penetration zones in 1D models with measurable acoustic glitches.
In a future paper, we will produce more realistic models by building upon our parameterization to include the crucial effects of density stratification.

@@

To find the extent of the penetrative region we write Eqn.~\eqref{eqn:mesa_eqn} as
\begin{align}
	(1-f) \int_{\rm CZ} L_{\rm conv} dr = \int_{\rm PZ} \left(\xi f L_{\rm conv,avg,CZ} + L_{\rm conv}\right) dr,
	\label{eq:rwt}
\end{align}
where $L_{\rm conv,avg,CZ}$ is the average of $L_{\rm conv}$ in the convection zone and $L_{\rm conv}$ in the penetrative region is given by
\begin{align}
	L_{\rm conv} = \frac{L_{\rm rad}}{\nabla_r}(\nabla_a - \nabla_r),
\end{align}
which is the excess luminosity carried if the temperature gradient in the radiative zone is adiabatic.

@@

\section{Table of simulation parameters}
\label{app:simulation_table}
Input parameters and summary statistics of the simulations presented in this work are shown in Table~\ref{table:simulation_info}.

@@

\newpage
\,
\newpage
\bibliographystyle{aasjournal}
\bibliography{biblio}
\end{document}
